# Reproducible Research: Peer Assessment 1
```{r,echo=FALSE}
setwd("D:/Document/My Copy/Copy/Portable Python 2.7.3.2/App/Scripts/repdata-002/RepData_PeerAssessment1")
```


## Loading and preprocessing the data
```{r,warning=FALSE}
unzip("activity.zip", overwrite=FALSE);
activity = read.csv("activity.csv" ,header=TRUE);
activity$date = as.Date(activity$date, "%Y-%m-%d");
```



## What is mean total number of steps taken per day?
```{r}
steps = activity[!is.na(activity$steps),];
total = tapply(steps$steps, steps$date, sum);
hist(total, breaks=25, col="red", xlab=" Total number of steps each day", main="")
```
The mean total number of steps taken per day is
```{r}
mean(total)
```
The median total number of steps taken per day is
```{r}
median(total)
```


## What is the average daily activity pattern?
```{r}
m =  aggregate(steps$steps, by=list(steps$interval), FUN=mean);
plot(m$Group.1,m$x, type = "l", ylab="Average number of steps ", xlab="Interval")
```
The 5-minute interval contains the maximum number of steps is 
```{r}
m[,1][which(m[,2]==max(m[,2]))]
```



## Imputing missing values
The total number of missing values in the dataset is
```{r}
sum(is.na(activity$steps))
```
Create a new dataset by replacing the `NA`s using the mean of 5-minute interval.
```{r}
t = merge(activity, m, by.x="interval", by.y="Group.1", all=TRUE);
t$steps = ifelse(is.na(t$steps), t$x, t$steps);
new =t[,1:3]
```
Now repeat the Part 1 to see the difference
```{r}
total = tapply(new$steps, new$date, sum);
hist(total, breaks=25, col="red", xlab=" Total number of steps each day", main="")
```
The mean total number of steps taken per day is
```{r}
mean(total)
```
The median total number of steps taken per day is
```{r}
median(total)
```


## Are there differences in activity patterns between weekdays and weekends?
Create a new factor variable in the dataset with two levels -- "weekday" and "weekend" indicating whether a given date is a weekday or weekend day.
```{r}
new$weekend = ifelse(as.POSIXlt(new$date)$wday==6 | as.POSIXlt(new$date)$wday==0, 1, 0);
new$weekend = factor(new$weekend, label=c("weekday","weekend"));
m = aggregate(new$steps, by = list(new$interval,new$weekend), FUN = mean)
```
Make a panel plot containing both weekend and weekday activity patterns
```{r,message=FALSE}
require("lattice");
xyplot(x ~ Group.1|Group.2, data=m, type="l", layout = c(1,2), ylab="Number of Steps", xlab="interval" )
```



